\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-14 doc/sw-system.tex
Resolved all AV's comments #209

During the \StageOne classification of the \cfhtls images, we assigned a prior
probability for each image to contain a lens of $2\times10^{-4}$, based on a
rough estimate of the number of expected lenses in the survey, and the fraction
of the survey area covered by each image. We then assigned two values of the
images' posterior probability, $\pr(\LENS|C,T)$, to define ``detection'' and
``rejection'' thresholds. These were set to be 0.95 and (approximately
symmetrically in the logarithm of probability), $10^{-7}$. Subjects that
attained probability of less than the rejection threshold were scheduled for
retirement and subsequently ignored by the analysis code. Subjects crossing the
detection threshold were also subsequently ignored, but they were not
retired from the website, just so that more volunteers could see them.

@@

\flag{AV}{MENTION HARDER TRAINING HERE MEANING THAT THE SPREAD IS LARGER?}

@@

We investigated the source of the incompleteness and impurity visible in
\Fref{fig:results:sample:CP}, by examining the \StageTwo false negatives and
false positives, and their behaviour as they are classified using the online
analysis trajectory plots introduced in \Sref{sec:swap}
(\Fref{fig:swap:subject-trajectories}).
\Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses
that were missed ($\pr(\LENS|C,T) < 10^{-7}$) by the \SW system (top row),
and 2 example
non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
0.95$) by the \SW system (bottom row).

@@

Some of  the mistakes made by reasonably high skill classifiers working at high
speed could have perhaps been corrected by those classifiers themselves, had
they had access to a ``go back'' option. While clearly enabling error reduction, particularly those caused by simply skimming too fast,
we might worry about such a mechanism enabling classifiers to have a guess, then
go and read the \Talk discussion, and then return to the classification
interface to change their mind to agree with the forum. In fact, this is already
possible on the current interface -- and indeed, it is not obvious that such
correlations would necessarily lead to poorer system performance.
\flag{AV}{REPETITION OF
TALK FACTOR FROM EARLIER SECTION, IT"S NOT NEEDED TWICE}. There may well
also be effects on volunteer confidence; it may be that encouraging this sort of
checking would result in increased and not necessarily productive caution. This
could be tested by presenting a fraction of the volunteers with a version of the
site that actively suggested that they take this approach, and then tracking the
relative performance of ``collaborative'' classifications compared with
independent ones. We leave the exploration of this to further work.

@@

However, identification failures \flag{AV}{DEFINE WHAT YOU MEAN BY IDENTIFICATION
FAILURES} around 60\%, from inspection of a random sample) seem to be due to the
statistical noise associated with the many short, semi-random direction kicks
arising from classifications made by low skill, inexperienced classifiers
(\Sref{sec:results:crowd}). \flag{AV}{ARE YOU SAYING THAT THERE ARE MORE OF THESE THAN THE
RIGHT COLUMN EXAMPLES?  WE SHOULD GIVE NUMBERS.} While improved training will
help reduce this effect, it is here that targeted task assignment could also
help improve system performance, by bringing higher skill volunteers in when
needed. We advertised \StageTwo of the current project to all registered users;
it was taken up by \StageOne veterans with a broad range of skill, and also
picked up a significant number of new users who did not have enough time to
acquire high skill (since \StageTwo was quite short): of the 1964 volunteers who
took part in the \StageTwo classification round, only 774 were veterans from
\StageOne.

>>>>

During the \StageOne classification of the \cfhtls images, we assigned a prior
probability for each image to contain a lens of $2\times10^{-4}$, based on a
rough estimate of the number of expected lenses in the survey, and the fraction
of the survey area covered by each image. We then assigned two values of the
images' posterior probability, $\pr(\LENS|C,T)$, to define ``detection'' and
``rejection'' thresholds. These were set to be 0.95 and (approximately
symmetrically in the logarithm of probability), $10^{-7}$. Subjects that
attained probability of less than the rejection threshold were scheduled for
retirement and subsequently ignored by the analysis code. Subjects crossing the
$P=0.95$ detection threshold were also subsequently ignored, but they were not
retired from the website, just so that more volunteers could see them.

@@

@@

We investigated the source of the incompleteness and impurity visible in
\Fref{fig:results:sample:CP}, by examining the \StageTwo ``false negatives''
(simulated lenses that incorrectly acquired $P < 10^{-7}$) and
false positives (duds or impostors that incorrectly acquired $P > 0.95$),
and their behaviour as they are classified using the online
analysis trajectory plots introduced in \Sref{sec:swap}
(\Fref{fig:swap:subject-trajectories}).
\Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses
that were missed ($\pr(\LENS|C,T) < 10^{-7}$) by the \SW system (top row),
and 2 example
non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
0.95$) by the \SW system (bottom row).

@@

Some of  the mistakes made by reasonably high skill classifiers working at high
speed could have perhaps been corrected by those classifiers themselves, had
they had access to a ``go back'' option. While clearly enabling error reduction,
we might worry about such a mechanism having a negative effect on
volunteer confidence: it may be that encouraging this sort of
checking would result in increased and not necessarily productive caution. This
could be tested by presenting a fraction of the volunteers with a version of the
site that actively suggested that they take this approach, and then tracking the
relative performance of ``collaborative'' classifications compared with
independent ones. We leave the exploration of this to further work.

@@

However, many false negatives (around 60\%, from inspection of a random sample)
seem to be due to the statistical noise associated with the many short,
semi-random direction kicks arising from classifications made by low skill,
inexperienced classifiers (\Sref{sec:results:crowd}). While improved training
will help reduce this effect, it is here that targeted task assignment could
also help improve system performance, by bringing higher skill volunteers in
when needed. We advertised \StageTwo of the current project to all registered
users; it was taken up by \StageOne veterans with a broad range of skill, and
also picked up a significant number of new users who did not have enough time to
acquire high skill (since \StageTwo was quite short): of the 1964 volunteers who
took part in the \StageTwo classification round, only 774 were veterans from
\StageOne. This issue is discussed further in \PaperTwo, where we investigate
the known lenses missed by the \SW system.
